DNNNNR0: How to Avoid OOTA Without Really Trying

### 2025-05-11 paper/ootavacuous.tex
ootavacuous: Page-1 wordsmithing
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

	We focus on shared-memory programs and C++ implementations based
	on traditional compilers and hardware, including CPUs and GPGPUs,
	thus enabling analysis of semantic dependencies and OOTA behaviors
	by means of existing hardware models.
	We show that these models' constraints prevent OOTA cycles from
	occurring in undefined-behavior-free C++ programs running on
	such implementations, provided the cycles involve only volatile
	atomics.
	We accommodate nonvolatile atomics by defining ``quasi-volatile''
	behavior which enables existing implementations that do per-thread
	analysis and optimization not only to avoid OOTA, but also to
	avoid incorrectly evaluating arithmetic expressions involving
	atomic accesses.

@@

>>>>

	We focus on shared-memory programs and C++ implementations based
	on traditional compilers and hardware, including CPUs and GPGPUs,
	thus enabling analysis of semantic dependencies and OOTA behaviors
	by means of existing hardware models.
	We show that these models' constraints prevent OOTA cycles from
	occurring in undefined-behavior-free C++ programs running on
	such implementations, provided the cycles involve only volatile
	atomics.
	We accommodate nonvolatile atomics by defining ``quasi-volatile''
	behavior and show that existing implementations doing per-thread
	analysis and optimization not only avoid OOTA, but also avoid
	incorrectly evaluating arithmetic expressions involving atomic
	accesses.

@@

This paper is a condensation of P3064R2 ("How to Avoid OOTA Without
Really Trying")~\cite{PaulEMcKenney2023P3046R2/OOTAwithoutTrying},
which was criticized as being overly long.
It also adds citations and clarifications.
